\documentclass[11pt]{article}
%
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{geometry}
 \geometry{
 a4paper,
 left=25mm,
 right=25mm,
 top=34mm,
 bottom=34mm}
\usepackage{tocloft}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{array}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}


\begin{document}
%
\title{Threshold Signatures: Efficient Constructions and Applications in Blockchains}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Zhuo Cai\\Department of Computer Science and Engineering\\Hong Kong University of Science and Technology}
%
% \authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Threshold signature schemes are important cryptographic primitives. Due to its importance in distributed systems and real applications, threshold signatures have been studied since late 1980s. In recent years, threshold signatures received research attention again, with application in cryptocurrencies, because classical threshold signatures, such as BLS threshold signatures, are not practical for large-scale applications and dynamic distributed systems. Recent hot topics in threshold signatures include (1) succinct signatures using SNARKs, (2) efficient DKG setup protocols for threshold signatures, (3) applications of multi-signatures in blockchain applications and (4) adaptive security, minimal assumptions, and other theoretical aspects of threshold signatures. This survey presents the basic components of threshold signatures and discusses a few recent works on different directions. Finally, the survey suggests some new directions for future research. 
\end{abstract}
%
%
\newpage
\tableofcontents

\newpage
\input{intro.tex}

\newpage
\input{basic.tex}

\newpage
\input{threshold.tex}

\newpage
\input{dkg.tex}

\newpage
\input{weighted.tex}

\newpage
\input{topic1.tex}

\newpage
\input{topic2.tex}

\newpage
\input{topic3.tex}

\newpage
\section{Conclusion}
This survey presents classical and SNARK-based threshold signature schemes. Threshold signatures are essential in distributed systems and cryptocurrencies. Although research on threshold signatures started from more than 30 years ago, there are challenges that are not addressed enough, some of which arising from the latest emgerging application scenarios. There are a large body of works on threshold signatures, so that I cannot cover every aspect of threshold signature research, nor cover the details of latest relevant protocols.  However, this survey covers the components and constructions of classical threshold signatures, mentions other related terms that might be useful for interested readers. As for future research, this survey suggests a few promising directions, including improving aggregate signatures using SNARKs, designing efficient incremental DKG and ambitiously proposing a new cryptographic paradigm for threshold signatures with an arbitrary threshold. 


% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}

\newpage

\bibliographystyle{splncs04}
\bibliography{reference}

\end{document}
