\section{Future Works}
%\frame{\tableofcontents[currentsection]}


\begin{frame}{Topic 1: succinct aggregate signatures and democratic voting}
\textbf{Aggregate Signatures}  $n$ members may sign different messages. $P_i$ creates a signature for $m_i$: $H(m)^{x_i}$. \\
How to aggregate these signatures to one short proof? \\
\vspace{0.5em}
\pause 
\textbf{Democratic voting} Suppose the group votes for a leader and there are multiple candidates. \\
A candidate wins if he receives the most votes, not necessarily $>50\%$. \\
A proof of candidate winning with $40\%$ votes should show that all other candidates receives $<40\%$ votes. \\
\pause 
\vspace{0.5em}
Generic SNARK works, maybe special SNARKs can make further improvement. 
\end{frame}

\begin{frame}{Topic 2: incremental DKG}
    If only a few new members join or a few old members leave, can we do better than rerun the complete DKG protocol again (the total communication cost is $O(\kappa n^3))$? \\
\end{frame}

\begin{frame}{Topic 3: alternative multi-threshold cryptosystem}
    Current (BLS) threshold signatures are based on signatures where verification result is binary. \\
    A signature is either valid or invalid. \\
    \vspace{0.5em} 
    What if the verification step returns a value in range $[0,1]$? \\
    Discrete log cryptography might not achieve this. What about lattice cryptography, or another family of hard problems?  
\end{frame}



\begin{frame}{Summary}
    \begin{itemize}
        \item BLS threshold signature, based on BLS signature and secret sharing.
        \item Weighted, multi-threshold TS, based on generic/special SNARKs.
        \item DKG, efficient asynchronous DKG, incremental DKG. 
        \item Alternative multi-threshold cryptosystem. 
    \end{itemize}
\end{frame}