
\section{Introduction}
%\frame{\tableofcontents[currentsection]}

\begin{frame}
\frametitle{Background: Digital Signatures}

In cryptocurrencies, everyone has a pair of public/secret keys. \\
Alice has $\mathsf{pk}_A$ and $\mathsf{sk}_A$.  Others know $\mathsf{pk}_A$, but only Alice knows $\mathsf{sk}_A$. \\
\begin{examples}
    Alice wants to pay 1 coin to Bob and propagates a message ``Alice pays 1 coin to Bob''. \\
    Can Alice spend Bob's coin by broadcasting ``Bob pays 2 coins to Alice''? \\
\end{examples}
\pause
Alice should not be able to add the message to blockchain. \\ \pause
\vspace{1em}
How can we prevent Alice from spending Bob's coins? \\ \pause
- Alice should sign on her message: a digital signature $\sigma_A$ generated using secret key $\mathsf{sk}_A$, and can be verified using $\mathsf{pk}_A$. \\ \pause
- Alice cannot forge Bob's signature to spend Bob's coins. 

\end{frame}



\begin{frame}
    \frametitle{Multi Signatures}
    Alice and Bob jointly own a coin $c$. Only if Alice and Bob both agree, the coin $c$ can be spent. \\ \pause
    Solution: 
    \begin{itemize}
        \item Alice signs on $m=$``A\&B transfer coin $c$ to Carol'': $\sigma_A(m)$. 
        \item Bob also signs on $m=$``A\&B transfer coin $c$ to Carol'': $\sigma_B(m)$. 
        \item (Verification): The miner includes $m$ only if he sees both $\sigma_A(m)$ and $\sigma_B(m)$. 
    \end{itemize}
    \begin{block}{Multi Signatures} 
        For a group of $n$ members, $\{P_1, P_2,\dots, P_n\}$, a signature is valid if only if all $n$ members all agree to generate it.  
    \end{block}
    \end{frame}
    
    \begin{frame}{Threshold Signatures}
    Alice, Bob and Carol are committee members of company that controls many coins. {\color{red} Any two of them} can spend these coins. \\ \pause 
    Solution: (When Alice and Carol agree to donate a coin to HKUST) 
    \begin{itemize}
        \item Alice and Carol each signs on $m$: $\sigma_A(m), \sigma_C(m)$. 
        \item (Verification): the miner includes $m$ if he sees two of $\{\sigma_A(m),\sigma_B(m), \sigma_C(m)\}$. 
    \end{itemize}
    \begin{block}{Threshold Signatures} 
        For a group of $n$ members, $\{P_1, P_2,\dots, P_n\}$, a signature is valid if only if a subset of \textit{at least} $t$ members agree to generate it.  
    \end{block}
    \end{frame}



\begin{frame}{Efficiency}
    Is the previous na\"ive threshold signature efficient? ($t=\Theta(n)$ e.g. $t=(n-1)/2$)\\
    \begin{itemize}
        \item Signature generation time: $\Theta(n)$. 
        \item Signature size: $\Theta(n)$. 
        \item Verification time: $\Theta(n)$. 
    \end{itemize}
    \pause 
    
    Settings: 
    \begin{itemize}
    \item  A signature is verified many times (all blockchain nodes have to verify each transaction). \\
    - Try reducing the signature size/verification time, even at the cost of slow generation time. \pause 
    \item The group might generate many signatures! \\
    - Try reducing the cost of each signature (Gen+Ver), even at the cost of some expensive setup/precomputation. 
    \end{itemize}
    \end{frame}
    